---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BMABMDR

<!-- badges: start -->
<!-- badges: end -->

BMABMDR is an R package for Bayesian model averaging in benchmark dose estimation. Its two main functions are:

* `full.laplace_MA()` to perform model averaging using Laplace approximation

* `sampling_MA()` to perform model averaging using Bridge sampling

## Installation

You can install the development version of BMABMDR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cecilekremer/BMABMDR")
```

## Example

This is a basic example which shows you how to use the package:

```{r example}
library(BMABMDR)

## Set summary data

summ.data <- data.frame(x = c(0,0.5,1,2,3),
                        y = c(7.534954, 10.500018, 13.886423, 15.192057, 15.331456),
                        s = c(0.3131743, 0.6299896, 0.8874875, 0.8709575, 0.8501652),
                        n = c(20, 20, 20, 20, 20))

## Check if there is a dose-response effect

anydoseresponseN(summ.data$x, summ.data$y, summ.data$s, summ.data$n)
anydoseresponseLN(summ.data$x, summ.data$y, summ.data$s, summ.data$n)

## Prepare data to pass to main functions

data_N <- PREP_DATA_N(data = summ.data,
                       sumstats = TRUE, sd = TRUE, q = 0.05)
data_LN <- PREP_DATA_LN(data = summ.data,
                       sumstats = TRUE, sd = TRUE, q = 0.05)

## Perform model averaging using Laplace approximation

# We include only Family 1 for the Normal distribution in this example
FLBMD <- full.laplace_MA(data_N, data_LN, prior.weights = c(rep(1, 4), rep(0, 12)))

# Plot results
pFLBMD <- plot.BMADR(FLBMD, type = 'increasing', weight_type = 'LP', title = '')
pFLBMD$BMDs
pFLBMD$weights
pFLBMD$model_fit_N
pFLBMD$MA_fit

## Perform model averaging using Bridge sampling

SBMD <- sampling_MA(data_N, data_LN, prior.weights = c(rep(1, 4), rep(0, 12)))

# Plot results
pSBMD <- plot.BMADR(SBMD, type = 'increasing', weight_type = 'BS', title = '')

```

## Getting help

If you encounter a bug, please file an issue with a minimal reproducible example on [GitHub](https://github.com/cecilekremer/BMABMDR/issues).


